Rank Verification in Exponential Families

### 2017-07-19 slides.tex
minor update before poster

\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{natbib}
\usepackage{lmodern}
\usepackage{tikz}
\usetikzlibrary{calc}
\usepackage{xcolor}
\definecolor{mid_purple}{HTML}{B894B1}

@@

\author[Kenneth Hung]{Kenneth Hung}
\institute[UC Berkeley]{
University of California, Berkeley \\
\medskip
\textit{kenhung@berkeley.edu}
}
\date{June 23, 2017 @ MCP2017}

@@

\begin{frame}{Related work}
\begin{itemize}
\item Ranking and selection: \citet{Gupta:1971wk,Gupta:1985bj,Gutmann:1987fk}
\item Location-scale families: \citet{Gutmann:1987fk,Bofinger:1991hv,Maymin:1992fz,Karnnan:2009iv}
\item CSB for location family using partition: \citet{Stefansson:1988wj}
\item Multinomial families: \citet{Gupta:1967wg,Gupta:1976vd,Berger:1980ev,Nettleton:2009ht,Gupta:1989fe,Ng:2007cn,Gupta:1967wg}

\item Conditional selective inference: \citet{Fithian:2014ws}
\end{itemize}
\end{frame}

@@

\begin{frame}[allowframebreaks]{References}
\footnotesize{\bibliography{papers}\bibliographystyle{plainnat}}
\end{frame}

>>>>

\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{lmodern}
\usepackage{tikz}
\usetikzlibrary{calc}
\usepackage{xcolor}
\definecolor{mid_purple}{HTML}{B894B1}

@@

\author[Kenneth Hung]{Kenneth Hung}
\institute[UC Berkeley]{
University of California, Berkeley \\
\medskip
\textit{kenhung@berkeley.edu}
}
\date{[Insert date]}

@@

\begin{frame}{Selected related work}
\begin{itemize}
\item Test for log-concave location families: \citet{Gutmann:1987fk}
\item Test for scale and location-scale families: \citet{Bofinger:1991hv,Maymin:1992fz,Karnnan:2009iv}
\item Test and lower bound for log-concave location families, using partition principle from \citet{Finner:2002ju}: \citet{Stefansson:1988wj}
\item Multinomial families: \citet{Gupta:1967wg}
\item Conditional selective inference: \citet{Fithian:2014ws}
\end{itemize}
\end{frame}

@@

\begin{frame}[allowframebreaks]{References}
\footnotesize{
\bibliography{papers}
\bibliographystyle{plainnat}
}
\end{frame}
